---
title: 'Capstone: Yelp Data Analysis'
author: "Sau-Chin Chen"
output: html_document
---
```{r initial, cache.path="../Yelp_Data", echo=FALSE, results='hide', warning=FALSE, message=FALSE}
source("./packageskit.R")
load("../Yelp_Data/Raw.RData")
```

# Get Data

This project will analyze the data set from [Yelp Dataset Challenge](http://www.yelp.com/dataset_challenge). The data set is downloaded from [this link](https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/yelp_dataset_challenge_academic_dataset.zip). I obtained and pre-processed the data set through the codes in [0GetData.R](0GetData.R). Here are files compressed in the zip file:

```{r overview, cache.path="../Yelp_Data", echo=FALSE, warning=FALSE}
print(unzip("../Yelp_Data/yelp.zip", list = TRUE))
```

Yelp is collecting the users' review for the businesses around the major cities across North America and Europe. Data set *business* collects the information from `r dim(yelp_business)[1]` businesses. Data set *checkin* stores `r dim(yelp_checkin)[1]` durations and frequencies a user stay in every business. Data set *review* sumarizes `r dim(yelp_review)[1]` reviews for a registed business. Data set *tip* summarizes the `r dim(yelp_tip)[1]` recommendations for a business. Data set *user* collects the information from  `r dim(yelp_user)[1]` registed users.